Application of Equal Local Levels to Improve Q-Q Plot Testing Bands with \proglang{R} Package \pkg{qqconf}

### 2021-05-02 article/manuscript.tex
made article changes, fixed dparams bug in code

A number of methods have been created towards this end. Naively, one could put pointwise testing bands onto Q-Q plots, which conduct $\alpha$ level tests on each order statistic of the sample. This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution. To appropriately deal with this multiple testing problem, the Komolgorov-Smirnov (KS) statistic is commonly used to create joint testing bands \citep{kolmogoroff1941confidence, smirnov1944approximate}. While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power, berk1979goodness}. A more promising approach would be to apply the equal local levels method (ELL) to create testing bands. This method, originally introduced by Berk and Jones and later developed by Gontscharuk et al. as an alternative testing procedure to higher-criticism and KS, conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness, gontscharuk2017asymptotics}. Because this test conducts an $\eta$ level test on each order statistic, it can be used to create testing bands that are agnostic to any alternative distribution. While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test to use in creating testing bands on Q-Q plots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.

@@

Currently, there is no available software that allows a user to quickly create plausible and robust testing bands for Q-Q plots on real data. While the base-\proglang{R} package \pkg{stats} provides functionality for creating a Q-Q plot to compare a sample against the normal distribution, it doesn't give the user the ability to create Q-Q plots for other distributions or to put testing bands on those plots. The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create Q-Q plots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}. However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes.

@@

%Add a line about Alder Noiman here where you mention tail sensitive and qqplotr

>>>>

A number of methods have been created towards this end. Naively, one could put pointwise testing bands onto Q-Q plots, which conduct $\alpha$ level tests on each order statistic of the sample. This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution. To appropriately deal with this multiple testing problem, the Komolgorov-Smirnov (KS) statistic is commonly used to create joint testing bands \citep{kolmogoroff1941confidence, smirnov1944approximate}. While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power, berk1979goodness}. A more promising approach would be to apply the equal local levels method (ELL) to create testing bands. This method, originally introduced by Berk and Jones and later developed by Gontscharuk et al. as an alternative testing procedure to higher-criticism and KS, conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness, gontscharuk2017asymptotics}. Because this test conducts an $\eta$ level test on each order statistic, it can be used to create testing bands that are agnostic to any alternative distribution. While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test in this use case, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.

@@

Currently, there is no available software that allows a user to quickly create plausible and robust testing bands for Q-Q plots on real data. While the base-\proglang{R} package \pkg{stats} provides functionality for creating a Q-Q plot to compare a sample against the normal distribution, it doesn't give the user the ability to create Q-Q plots for other distributions or to put testing bands on those plots. The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create Q-Q plots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}. Specifically, for the normal distribution \pkg{qqplotr} implements a simulation based method called tail sensitive (TS) testing bands, originally developed by Alder-Noiman \citep{aldor2013power}.  However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes because it uses simulation.

@@
